Modelling BCG vaccination in the UK

### 2019-08-06 rmds/10-model-results.Rmd
update word count
acronyms updated

@@

## Forecasting the long-term impact of each vaccination scenario.

@@

```{r 10-age-scenarios-deaths-fig, fig.scap = "Forecast TB mortality for each scenario evaluated from 2005 to 2040, stratified by age group, stratified by age group.", fig.cap = "Forecast TB mortality for each scenario evaluated from 2005 to 2040, stratified by age group (0-11). 0-9 refers to 5 year age groups from 0-4 years old to 45-49 years old. 10 refers to those aged between 50 and 69 and 11 refers to those aged 70+. Scenarios are differentiated by colour. The darker ribbon for each colour identifies the interquartile range, whilst the lighter ribbon indicates the 2.5\\% and 97.5\\% quantiles. The line represents the median."}
knitr::include_graphics(file.path(plots_path, "overview-scenarios-deaths-future-age-1.png"))
```
### Summary

>>>>

## Wordcount: 2293

@@

### Forecasting the long-term impact of each vaccination scenario.

@@

```{r 10-age-scenarios-deaths-fig, fig.scap = "Forecast TB mortality for each scenario evaluated from 2005 to 2040, stratified by age group, stratified by age group.", fig.cap = "Forecast TB mortality for each scenario evaluated from 2005 to 2040, stratified by age group (0-11). 0-9 refers to 5 year age groups from 0-4 years old to 45-49 years old. 10 refers to those aged between 50 and 69 and 11 refers to those aged 70+. Scenarios are differentiated by colour. The darker ribbon for each colour identifies the interquartile range, whilst the lighter ribbon indicates the 2.5\\% and 97.5\\% quantiles. The line represents the median."}
knitr::include_graphics(file.path(plots_path, "overview-scenarios-deaths-future-age-1.png"))
```

## Discussion
